Limits to Ecological Forecasting: Estimating Uncertainty for Critical Transitions with Deep Learning

### 2022-08-05 manuscript/manuscript.Rmd
Tidying new intro paragraph

“In this paper, we focus on the task of producing quantitative, probabilistic forecasts reflecting the possible distribution of future states at some time in the future.  It is important to distinguish this objective from the extensive previous literature on “early warning signs” of critical transitions [eg as reviewed in @Scheffer2015] which has sought to answer only a categorical question: is the system approaching a critical transition? More recent work by @Bury2021 has introduced ML methods to consider classification of this transition in four possible categories (Hopf, saddle-node, transcritical, or no bifurcation) rather than two (bifurcation or not). These are important results with considerable success, but do not answer the questions of when a shift might occur or how large that transition will be. In light of increasing calls for the importance of such quantitative, probabilistic forecasts [@Deitz2018], we focus on evaluating the potential and limits to prediction in critical transition scenarios.”

>>>>

In this paper, we focus on the task of producing quantitative, probabilistic forecasts reflecting the possible distribution of future states.  It is important to distinguish this objective from the extensive previous literature on “early warning signs” of critical transitions, as reviewed in @scheffer_early-warning_2009, which has sought to answer only a categorical question: is the system approaching a critical transition? More recent work by @bury_2021 has introduced ML methods to consider classification of this transition in four possible categories (Hopf, saddle-node, transcritical, or no bifurcation) rather than two (bifurcation or not). These are important results with considerable success, but do not answer the questions of when a shift might occur or how large that transition will be. In light of increasing calls for the importance of such quantitative, probabilistic forecasts [@dietze_iterative_2018], we focus on evaluating the potential and limits to prediction in critical transition scenarios.
